Experiment 1

### 2024-03-22 Analysis/e1.qmd
remove more docusaurus related items, and re-render e1 analysis

---
title: "Experiment 1"
categories: [Analyses, R, Bayesian]
toc: false
format-links: false
page-layout: full
code-fold: true
cold-tools: true
lightbox: true
execute:
  #cache: true
  warning: false
format:
  html: default
  # hugo-md:
  #   echo: false
  #   html-math-method: mathjax
  #   output-file: e1-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e1-gfm.md
  # docusaurus-md:
  #   echo: true
  #   output-file: e1-docusaurus.md
#prefer-html: false
---

>>>>

---
title: "Experiment 1"
categories: [Analyses, R, Bayesian]
toc: false
format-links: false
page-layout: full
code-fold: true
cold-tools: true
lightbox: true
execute:
  warning: false
format:
  html: default
  # hugo-md:
  #   echo: false
  #   html-math-method: mathjax
  #   output-file: e1-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e1-gfm.md
  # docusaurus-md:
  #   echo: true
  #   output-file: e1-docusaurus.md
#prefer-html: false
---
